---
title: "CyclisticBikeShare_Project_02"
author: "Le Thi Thanh Tam"
date: "3/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# How do annual members and casual riders use Cyclistic bikes differently ?

```{r message=FALSE, error= FALSE, results='hide'}
#get the default working directory of R
getwd()
#set the desired working directory of R
setwd('E:/ThanhTam_DA/Cyclistic_Data')
#remove all the objects 
rm(list = ls())
#clear the console
cat("\014")
#clear the plots
dev.off()
```


```{r message = FALSE }
# Install required packages
# tidyverse for data import and wrangling
# libridate for date functions
# ggplot for visualization
library(tidyverse)  #helps wrangle data
library(lubridate)  #helps wrangle date attributes
library(ggplot2)  #helps visualize data
```
## Import the datasets

```{r}
## The Cyclistic’s historical trip data is collected by every months, we will work on dataset from 2021/04 to 2022/02
# Import data 
tripdata042021 <- read.csv("202104-divvy-tripdata.csv")
tripdata052021 <- read.csv("202105-divvy-tripdata.csv")
tripdata062021 <- read.csv("202106-divvy-tripdata.csv")
tripdata072021 <- read.csv("202107-divvy-tripdata.csv")
tripdata082021 <- read.csv("202108-divvy-tripdata.csv")
tripdata092021 <- read.csv("202109-divvy-tripdata.csv")
tripdata102021 <- read.csv("202110-divvy-tripdata.csv")
tripdata112021 <- read.csv("202111-divvy-tripdata.csv")
tripdata122021 <- read.csv("202112-divvy-tripdata.csv")
tripdata012022 <- read.csv("202201-divvy-tripdata.csv")
tripdata022022 <- read.csv("202202-divvy-tripdata.csv")
```

```{r}
# See the column names of each file to make sure they will be match perfectly before joinning data
colnames(tripdata012022)
colnames(tripdata022022)
colnames(tripdata042021)
colnames(tripdata052021)
colnames(tripdata062021)
colnames(tripdata072021)
colnames(tripdata082021)
colnames(tripdata092021)
colnames(tripdata102021)
colnames(tripdata112021)
colnames(tripdata122021)
# Internal structurer
str(tripdata012022)
str(tripdata022022)
str(tripdata042021)
str(tripdata052021)
str(tripdata062021)
str(tripdata072021)
str(tripdata082021)
str(tripdata092021)
str(tripdata102021)
str(tripdata112021)
str(tripdata122021)
```

```{r}
#Combine all data into a single dataset
all_trips <- rbind(tripdata042021,tripdata052021,tripdata062021,tripdata072021,tripdata082021,
                   tripdata092021,tripdata102021,tripdata112021,tripdata122021,tripdata012022,
                   tripdata022022)
```

```{r}
# Inspect the new table
colnames(all_trips)
str(all_trips)
dim(all_trips)
head(all_trips)
summary(all_trips)
```

## Clean and Transform the data
```{r}
#We will work on the member_casual column. Let's take a look at the consistency of values in this
unique(all_trips$member_casual)
```

```{r}
# Format check 
head(all_trips[,c("started_at", "ended_at")])
## Convert to date type
## Add column date, month, year and weekday to dataset for further analyze
all_trips$date <- as.Date(all_trips$started_at)
all_trips$day_of_week <- format(as.Date(all_trips$date), "%A")
all_trips$day <- format(as.Date(all_trips$date), "%d")
all_trips$month <- format(as.Date(all_trips$date), "%m")
all_trips$year <- format(as.Date(all_trips$date), "%Y")
head(all_trips)
```

```{r}
# Add a new column "ride_length" to calculate in second
all_trips$ride_length <- difftime(all_trips$ended_at, all_trips$started_at)
```


```{r}
# Inspect the structure of dataset
str(all_trips)
is.factor(all_trips$ride_length)
is.numeric(all_trips$ride_length)
# Convert "ride_length" to numeric so we can run calculations
all_trips$ride_length <- as.numeric(as.character(all_trips$ride_length))
is.numeric(all_trips$ride_length)
min(all_trips$ride_length)
# There has negative datas in ride_length
# Create a new data with deleted negatives values in ride_length
all_trips_v2 <- all_trips[!(all_trips$ride_length < 0),]
min(all_strips_v2$ride_length)
```

## Descriptive Analysis
*The number of each ride type user
```{r}
table(all_trips_v2$member_casual)
```
In total of 5,439,347 users id, there has 2,456,602 casual users and 2,982,745 member users

*Ride length data

```{r}
summary(all_trips_v2$ride_length)
```
As we can see above the description of ride length data 75% riders ride for 1291 seconds but the maximum ride length is 3356649 seconds.

### Compare members and casual users according to ride length 
```{r}
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual, FUN = mean)
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual, FUN = median)
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual, FUN = max)
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual, FUN = min)
```


The average in ride length of casual riders is 1902s higher than member riders (807.7s)
The median ride length of casual riders is 949s, and member riders is 568s
The maximum ride time of casual riders (3356649s) is much higher than member riders (89998s)


### Next see the average ride time by each day for members and casual users
```{r}
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual + all_trips_v2$day_of_week, FUN = mean)
```

```{r}
# The day of week are out of order
all_trips_v2$day_of_week <- ordered(all_trips_v2$day_of_week, levels = c("Sunday","Monday", "Tuesday","Wednesday", "Thursday", "Friday", "Saturday"))
# Now run again
memory.size()
memory.limit()
memory.limit(size=56000)
aggregate(all_trips_v2$ride_length ~ all_trips_v2$member_casual + all_trips_v2$day_of_week, FUN = mean)
```

### Analyze ridership data by type and weekday
```{r}
# See the number of rides and average duration by type during weekday
all_trips_v2 %>% 
  mutate(weekday = wday(started_at, label = TRUE)) %>% 
  group_by(member_casual, weekday) %>% 
  summarise(number_of_riders = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual, weekday)
  
```

### Create Visualization for number of riders by type
* Number of riders on weekday
```{r fig.height=3}
# Create a graph to visualize the number of riders by ride type during weekday
all_trips_v2 %>% 
  mutate(weekday = wday(started_at, label = TRUE)) %>% 
  group_by(member_casual, weekday) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,weekday) %>% 
  ggplot(aes(x = weekday, y = number_of_rides, fill = member_casual)) + geom_col(position = "dodge")
```
From the chart above we can see the clearly difference only for casual users ride highly on Saturday and then Sunday Whereas member of users use bike at the almost constant rate during the week.

* Number of riders per day
```{r fig.width= 4, fig.width=7}
all_trips_v2 %>% 
  group_by(member_casual, day) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,day) %>% 
  ggplot(aes(x = day, y = number_of_rides,group = member_casual, color = member_casual)) + geom_line()
```
We can certainly say members use bikes more often than casual in general. 

* Number of riders per month
```{r fig.width= 4, fig.width=5}
all_trips_v2 %>% 
  group_by(member_casual, month) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,month) %>% 
  ggplot(aes(x = month, y = number_of_rides,group = member_casual, color = member_casual)) + geom_line()
```
From line plot above we can see members use bikes more often than casual however casual users have dramatic rise from June 2021 to August 2021. 

### Create Visualization for rider length
*Usage of ride type based on ride length per week
```{r fig.height= 3}
# Create a graph to visualize the average duration by type during weekday
all_trips_v2 %>% 
  mutate(weekday = wday(started_at, label = TRUE)) %>% 
  group_by(member_casual, weekday) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,weekday) %>% 
  ggplot(aes(x = weekday, y = average_duration, fill = member_casual)) + geom_col(position = "dodge")
```
The above graph shows the clearly understanding about the average ride length. Casual type users ride much longer and as expected weekend got the higher ride length than others.

*Usage of ride type based on ride length per day
```{r fig.width= 4, fig.width=5}
all_trips_v2 %>% 
  group_by(member_casual, day) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,day) %>% 
  ggplot(aes(x = day, y = average_duration,group = member_casual, color = member_casual)) + geom_line()
```
The graph above shows the big gap between casual and member type. casual users spent much more time per day in using bikes more than members.

*Usage of ride type based on ride length per month
```{r fig.width= 4, fig.width=5}
all_trips_v2 %>% 
  group_by(member_casual, month) %>% 
  summarize(number_of_rides = n(), average_duration = mean(ride_length)) %>% 
  arrange(member_casual,month) %>% 
  ggplot(aes(x = month, y = average_duration,group = member_casual, color = member_casual)) + geom_line()
```
Also we can see the result from table above, casual users spend much more time than member users per month using bike.



